Um Breve Estudo da Adição de um Quarto\\ Nível de Cache em Processadores Multicore

### 2009-06-17 disciplinas/cmp134/simics/relatorio/relat.tex
relatorio do trabalho com o simics

%
%  $Description: Author guidelines and sample document in LaTeX2e$
%
%  $Author: ienne, paulley $
%  $Date: 2002/04/15 11:20:59 $
%  $Revision: 1.0 $
%

\documentclass{ieee}

%------------------------------------------------------------------------- 
% 
% Use \documentclass[pagenumbers]{ieee}
%
% to produce page numbers, bottom centered, in the output. Default is 
% no page numbers for camera-ready copy.
%
%-------------------------------------------------------------------------

\usepackage{times}
\usepackage[latin1]{inputenc}
\usepackage[brazil]{babel}

@@

\author{Carlos Eduardo B. Bezerra, Cláudio F. R. Geyer\\
Institudo de Informática\\
Universidade Federal do Rio Grande do Sual\\
Av. Bento Gonçalves, 9500, Porto Alegre, RS\\
\{carlos.bezerra, geyer\}@inf.ufrgs.br\\
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\ Second line of institution2 address\\ 
% SecondAuthor@institution2.com\\
}

>>>>

\documentclass[12pt]{article}

\usepackage{sbc-template}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx,url}

% \usepackage{subfig}

\usepackage{graphics}
%\usepackage{math}
%\usepackage{mathaccent}

\usepackage[brazil]{babel}   
\usepackage[latin1]{inputenc}

%\usepackage{times}
%\usepackage[latin1]{inputenc}
%\usepackage[brazil]{babel}

@@

\author{Carlos Eduardo Benevides Bezerra\inst{1}, Cláudio Fernando Resin Geyer\inst{1}}
\address{Instituto de Informática -- Universidade Federal do Rio Grande do Sul\\
  Caixa Postal 15.064 -- 91.501-970 -- Porto Alegre -- RS -- Brasil
}
